---
title: "clean_data"
format: html
---

```{r}
# Set time zone
Sys.setenv(TZ='Europe/London')

# Download and attach standard packages
if (!require(pacman)) {
  install.packages("pacman")
}

pacman::p_load(tidyverse, here, janitor, RMariaDB, DBI, glue, renv, dbplyr, lubridate, scales)

i_am("R/clean_modifiable_risk_factors.qmd")
```

```{r}
# Connect to CPRD database -------------------

# Connect to the MySQL database: con
con <- dbConnect(RMariaDB::MariaDB(), 
                 dbname = "cprd2023", 
                 host = "cprd-sea-2023.cisllnygqz7r.eu-west-2.rds.amazonaws.com", 
                 port = 3306,
                 user = "test",
                 password = "password")
```

## Smoking

Current smoker – the most recent smoking habit record within three years of the end date (i.e. from 1st April 2020 to end date) is a current smoking code

### Examine

```{r}
# Check cluster_ids for obesity

dbGetQuery(con, "SELECT DISTINCT(cluster_id) FROM p068_codes WHERE category IN ('Smoking status', 'Current smoker');")
```

```{r}
# Examine codes
codes <- dbGetQuery(con, "SELECT * FROM p068_codes WHERE category IN ('Smoking status', 'Current smoker');")

codes <- codes %>% 
    arrange(cluster_id)
```

```{r}
# Are all LSMOK codes in SMOK?
codes$medcodeid[codes$cluster_id == "LSMOK_COD"] %in% codes$medcodeid[codes$cluster_id == "SMOK_COD"]

# Drop SMOK_COD codes that are also in LSMOK_COD
dbExecute(con, "WITH t AS (
        SELECT medcodeid FROM p068_codes WHERE cluster_id = 'LSMOK_COD'
    )
    DELETE FROM p068_codes
    WHERE cluster_id = 'SMOK_COD'
    AND medcodeid IN (SELECT medcodeid FROM t);
    ")
```

```{r}
cohort_def_var <- "smoking"

# Examine table

# Print final number of distinct patients
dbGetQuery(con, glue("SELECT COUNT(DISTINCT patid), COUNT(*) FROM p068_{cohort_def_var}_define;"))
```

```{r}
# Count how often each medcode is used
dbGetQuery(con, glue("SELECT medcodeid_desc, COUNT(*) AS n_rows, medcodeid 
                     FROM p068_{cohort_def_var}_define 
                     GROUP BY medcodeid_desc
                     ORDER BY n_rows DESC;"))
```

```{r}
# Find max number of rows per patient
dbGetQuery(con, glue("SELECT patid, COUNT(*) AS n_rows
    FROM p068_{cohort_def_var}_define
    GROUP BY patid
    ORDER BY n_rows DESC
    LIMIT 10;"))
```

```{r}
dbGetQuery(con, glue("SELECT obstypeid, COUNT(*)
           FROM p068_{cohort_def_var}_define
           GROUP BY obstypeid
           ORDER BY COUNT(*) DESC"))
```

```{r}
smoking_df <- tbl(con, "p068_smoking_define")
```

```{r}
smoking_df %>% 
    count(category) %>% 
    arrange(desc(n))
```

```{r}
smoking_df %>% 
    count(cluster_id) %>% 
    arrange(desc(n))
```

```{r}
# Which codes are used the most in each cluster? (additional, LSMOK, SMOK)
smoking_codes_examine <- smoking_df %>% 
    group_by(cluster_id) %>% 
    count(medcodeid_desc) %>% 
    arrange(cluster_id, desc(n)) %>% 
    collect()
```

```{r}
# Investigate status records
smoking_status <- smoking_df %>% 
    filter(include == "Status") %>% 
    collect() %>% 
    arrange(medcodeid)
```


```{r}
# Look at status records
smoking_status %>% 
    count(medcodeid_desc, medcodeid) %>% 
    arrange(desc(n))

smoking_status %>% 
    count(numunitid) %>% 
    arrange(desc(n))
```
```{r}
tmp <- smoking_status %>% 
    filter(medcodeid == "342574011")
```

```{r}
# Investigate additional smoking codes that aren't smoking status records
smoking_additional <- smoking_df %>% 
    filter(include != "Status", cluster_id == "additional") %>% 
    collect()
```

```{r}
tmp <- smoking_additional %>%
    group_by(include) %>% 
    count(medcodeid_desc, medcodeid) %>% 
    arrange(include, desc(n))
```

### Execute

```{r}
#| eval: false

# Drop all records with additional codes for smoking status and intervention - not helpful
# Drop records before 1st Jan 1995
# Keep most recent record
# Drop records that are in SMOK_COD

dbExecute(con, "DROP TABLE IF EXISTS p068_smoker_mod_factor;")

smoker_query <- "CREATE TABLE p068_smoker_mod_factor
        WITH a AS ( -- Drop all records with include as smoking status or intervention, and before 1st Jan 1995
            SELECT *
            FROM p068_smoking_define
            WHERE include NOT IN ('Status', 'intervention')
            AND obsdate >= '1995-01-01'
        ),
        r AS ( -- Calculate row numbers per patient to keep latest record
            SELECT *,
            ROW_NUMBER() OVER (PARTITION BY patid ORDER BY obsdate DESC) AS rn
            FROM a
        )
        -- Keep latest record per patient
        -- Drop all records that are SMOK_COD (excluding SMOK_COD codes that are in LSMOK_COD)
        SELECT
            patid,
            pracid,
            obsid,
            obsdate,
            medcodeid,
            medcodeid_desc,
            value,
            numunitid,
            obstypeid,
            include,
            category,
            cluster_id
        FROM r
        WHERE rn = 1
        AND cluster_id NOT IN ('SMOK_COD');
    "

dbExecute(con, smoker_query)
```

### Examine post-execution

```{r}
# Check
tbl(con, "p068_smoker_mod_factor") %>% 
    count(medcodeid_desc, medcodeid) %>% 
    arrange(desc(n))

tbl(con, "p068_smoker_mod_factor") %>% 
    collect() %>% 
    summarise(n = n(),
              n_patid = n_distinct(patid),
              min_date = min(obsdate, na.rm = T),
              q1_date = quantile(obsdate, probs = 0.25, type = 1, na.rm = T),
              mean_date = mean(obsdate, na.rm = T),
              median_date = quantile(obsdate, probs = 0.5, type = 1, na.rm = T),
              q3_date = quantile(obsdate, probs = 0.75, type = 1, na.rm = T),
              max_date = max(obsdate, na.rm = T),
              n_na_date = sum(is.na(obsdate), na.rm = T))

```

```{r}
# Distribution of obsdate
tbl(con, "p068_smoker_mod_factor") %>%
    collect() %>%
    mutate(ym = ymd(paste0(year(obsdate), "-", month(obsdate), "-01"))) %>% 
    group_by(ym) %>% 
    summarise(n = n()) %>% 
    ggplot(aes(x = ym, y = n)) +
    geom_bar(stat = "identity") +
    scale_x_date(date_breaks="1 year", date_labels = "%b %Y", limits = c(ymd("1995-01-01", "2023-04-01"))) +
    scale_y_continuous(labels = label_comma()) +
    theme(axis.text.x = element_text(angle=90, vjust=.5, hjust=1)) 
```

## Obesity - classifications

Any record of a finding of BMI being obese, 30 or greater or 40 or greater, with no subsequent record of a finding of BMI being healthy, overweight or underweight within three years of the end date; or the most recent BMI value recording within three years of the end date having a value of 30 or greater

### Examine

```{r}
# Check cluster_ids for obesity

dbGetQuery(con, "SELECT DISTINCT(cluster_id) FROM p068_codes WHERE category IN ('Obese', 'Not obese');")
```


```{r}
cohort_def_var <- "obesity"

# Examine table

# Print final number of distinct patients
dbGetQuery(con, glue("SELECT COUNT(DISTINCT patid), COUNT(*) FROM p068_{cohort_def_var}_define;"))
```

```{r}
# Count how often each medcode is used
dbGetQuery(con, glue("SELECT medcodeid_desc, COUNT(*) AS n_rows, medcodeid 
                     FROM p068_{cohort_def_var}_define 
                     GROUP BY medcodeid_desc
                     ORDER BY n_rows DESC;"))
```

```{r}
# Find max number of rows per patient
dbGetQuery(con, glue("WITH t AS (
    SELECT patid, COUNT(*) AS n_rows
    FROM p068_{cohort_def_var}_define
    GROUP BY patid
    ORDER BY n_rows DESC
    LIMIT 5)
    SELECT MAX(n_rows) FROM t;"))
```

```{r}
# Examine codes
codes <- dbGetQuery(con, "SELECT * FROM p068_codes WHERE category IN ('Obese', 'Not obese');")

codes <- codes %>% 
    arrange(cluster_id)
```

```{r}
dbGetQuery(con, glue("SELECT obstypeid, COUNT(*)
           FROM p068_{cohort_def_var}_define
           GROUP BY obstypeid
           ORDER BY COUNT(*) DESC"))
```

```{r}
obesity_df <- tbl(con, "p068_obesity_define")
```

```{r}
obesity_df %>% 
    count(category) %>% 
    arrange(desc(n))
```

```{r}
obesity_df %>% 
    count(cluster_id) %>% 
    arrange(desc(n))
```

```{r}
obesity_df %>% 
    filter(category != "Not obese", !(cluster_id %in% c('BMIUNDER_COD', 'BMIHEALTHY_COD', 'BMIOVER_COD'))) %>% 
    count(medcodeid_desc) %>% 
    arrange(desc(n))
```

```{r}
# Obese records only
# Get number of rows
df_nrow <- obesity_df %>%
    filter(category != "Not obese", 
           !(cluster_id %in% c('BMIUNDER_COD', 'BMIHEALTHY_COD', 'BMIOVER_COD'))) %>% 
    summarise(n = n()) %>% 
    collect() %>% 
    pull(n) %>% 
    pluck(1)

# Min, mean and max date
obesity_df %>% 
    filter(category != "Not obese", 
           !(cluster_id %in% c('BMIUNDER_COD', 'BMIHEALTHY_COD', 'BMIOVER_COD'))) %>% 
    collect() %>% 
    summarise(min = min(obsdate, na.rm = T),
              q1 = quantile(obsdate, probs = 0.25, type = 1, na.rm = T),
              mean = mean(obsdate, na.rm = T),
              median = quantile(obsdate, probs = 0.5, type = 1, na.rm = T),
              q3 = quantile(obsdate, probs = 0.75, type = 1, na.rm = T),
              max = max(obsdate, na.rm = T))

# Count number of records before certain date
obesity_df %>% 
    filter(category != "Not obese", 
           !(cluster_id %in% c('BMIUNDER_COD', 'BMIHEALTHY_COD', 'BMIOVER_COD'))) %>% 
    collect() %>% 
    summarise(n = n(),
              n_na = sum(is.na(obsdate), na.rm = T),
              pre_1995 = sum(obsdate < ymd("1995-01-01"), na.rm = T),
              pre_2013 = sum(obsdate < ymd("2013-04-01"), na.rm = T),
              pre_2015 = sum(obsdate < ymd("2015-04-01"), na.rm = T),
              pre_2018 = sum(obsdate < ymd("2018-04-01"), na.rm = T),
              pre_2020 = sum(obsdate < ymd("2020-04-01"), na.rm = T),
              post_2023 = sum(obsdate > ymd("2023-03-31"), na.rm = T)) %>% 
    pivot_longer(cols = everything(), names_to = "var", values_to = "value") %>% 
    mutate(prop = value/df_nrow)
```


```{r}
# Distribution of obsdate
obesity_df %>% 
    filter(category != "Not obese", 
           !(cluster_id %in% c('BMIUNDER_COD', 'BMIHEALTHY_COD', 'BMIOVER_COD')),
           obsdate >= "1995-01-01",
           obsdate < "2023-04-01") %>% 
    collect() %>%
    mutate(ym = ymd(paste0(year(obsdate), "-", month(obsdate), "-01"))) %>% 
    group_by(ym) %>% 
    summarise(n = n()) %>% 
    ggplot(aes(x = ym, y = n)) +
    geom_bar(stat = "identity") +
    scale_x_date(date_breaks="1 year", date_labels = "%b %Y", limits = c(ymd("1995-01-01", "2023-04-01"))) +
    scale_y_continuous(labels = label_comma()) +
    theme(axis.text.x = element_text(angle=90, vjust=.5, hjust=1))
```

### Execute

```{r}
#| eval: false

# Rerun load data while filtering to exclude values for "Body mass index" (923861000006112) to another table
# Load those records in with bmival_define

# Keep latest record per person
# Remove records from BMIUNDER_COD, BMIHEALTHY_COD, BMIOVER_COD, category == "Not obese"
dbExecute(con, "DROP TABLE IF EXISTS p068_obese_classification;")

dbExecute(con, "CREATE TABLE p068_obese_classification
    SELECT *
    FROM p068_obesity_define
    WHERE category NOT IN ('Not obese')
    AND cluster_id NOT IN ('BMIUNDER_COD', 'BMIHEALTHY_COD', 'BMIOVER_COD')
    AND obsdate >= '1995-01-01';")
```


```{r}
# Print final number of distinct patients
dbGetQuery(con, glue("SELECT COUNT(DISTINCT patid), COUNT(*) FROM p068_obese_classification;"))

# Check date distribution
tbl(con, "p068_obese_classification") %>% 
    collect() %>% 
    summarise(min = min(obsdate, na.rm = T),
              q1 = quantile(obsdate, probs = 0.25, type = 1, na.rm = T),
              mean = mean(obsdate, na.rm = T),
              median = quantile(obsdate, probs = 0.5, type = 1, na.rm = T),
              q3 = quantile(obsdate, probs = 0.75, type = 1, na.rm = T),
              max = max(obsdate, na.rm = T))
```

## Obesity - BMI value

### Examine

```{r}
# Check cluster_ids for obesity

dbGetQuery(con, "SELECT DISTINCT(cluster_id) FROM p068_codes WHERE category IN ('BMI value');")
```


```{r}
cohort_def_var <- "bmival"

# Examine table

# Print final number of distinct patients
dbGetQuery(con, glue("SELECT COUNT(DISTINCT patid), COUNT(*) FROM p068_{cohort_def_var}_define;"))
```


```{r}
# Count how often each medcode is used
dbGetQuery(con, glue("SELECT medcodeid_desc, COUNT(*) AS n_rows 
                     FROM p068_{cohort_def_var}_define 
                     GROUP BY medcodeid_desc
                     ORDER BY n_rows DESC;"))
```


```{r}
# Find max number of rows per patient
dbGetQuery(con, glue("WITH t AS (
    SELECT patid, COUNT(*) AS n_rows
    FROM p068_{cohort_def_var}_define
    GROUP BY patid
    ORDER BY n_rows DESC
    LIMIT 5)
    SELECT MAX(n_rows) FROM t;"))
```



```{r}
# Examine obstypeid
dbGetQuery(con, glue("SELECT obstypeid, COUNT(*)
           FROM p068_{cohort_def_var}_define
           GROUP BY obstypeid
           ORDER BY COUNT(*) DESC"))
```

```{r}
# Examine numunitid
# Vast majority kg/m2
# Join didn't happen properly, strangely
dbGetQuery(con, glue("SELECT numunitid, COUNT(*)
           FROM p068_{cohort_def_var}_define
           GROUP BY obstypeid
           ORDER BY COUNT(*) DESC"))
```

```{r}
# Examine codes
codes <- dbGetQuery(con, "SELECT * FROM p068_codes WHERE category IN ('BMI value');")

codes <- codes %>% 
    arrange(cluster_id)
```

```{r}
# Create a table from bmival table in mySQL
bmival_df <- tbl(con, "p068_bmival_define")
```

```{r}
# Examine distributions
# Get number of rows
df_nrow <- bmival_df %>%
    summarise(n = n()) %>% 
    collect() %>% 
    pull(n) %>% 
    pluck(1)


# Summarise
bmival_df %>% 
    summarise(min = min(value, na.rm = T),
              mean = mean(value, na.rm = T),
              max = max(value, na.rm = T))

bmival_df %>% 
    summarise(n = n(),
              n_na = sum(is.na(value), na.rm = T),
              below_10 = sum(value < 10, na.rm = T),
              above_70 = sum(value > 70, na.rm = T)) %>% 
    pivot_longer(cols = everything(), names_to = "var", values_to = "value") %>% 
    mutate(prop = value/df_nrow)
```


```{r}
# Examine distributions for records between 0 and 70 only
# Summarise
bmival_df %>% 
    filter(between(value, 10, 70)) %>% 
    summarise(min = min(value, na.rm = T),
              mean = mean(value, na.rm = T),
              max = max(value, na.rm = T),
              n = n(),
              n_na = sum(is.na(value), na.rm = T))
```

```{r}
# Examine records with extreme values
small <- bmival_df %>% 
    filter(value < 10) %>% 
    collect()

large <- bmival_df %>% 
    filter(value > 70) %>% 
    collect()

nrow(small) + nrow(large)
```

```{r}

# Distribution after removing extreme values
bmival_df %>% 
    filter(between(value, 0, 100)) %>% 
    collect() %>% 
    ggplot(aes(x = value)) +
    geom_histogram(binwidth = 1) +
    scale_x_continuous(breaks = seq(0,100,5)) +
    scale_y_continuous(labels = label_comma())

bmival_df %>% 
    filter(between(value, 10, 70)) %>% 
    collect() %>% 
    ggplot(aes(x = value)) +
    geom_histogram(binwidth = 1) +
    scale_x_continuous(breaks = seq(0,100,5)) +
    scale_y_continuous(labels = label_comma())
```

```{r}
# Get number of rows
df_nrow <- bmival_df %>%
    filter(between(value, 10, 70)) %>% 
    summarise(n = n()) %>% 
    collect() %>% 
    pull(n) %>% 
    pluck(1)

bmival_df %>% 
    filter(between(value, 10, 70)) %>%
    collect() %>% 
    summarise(min = min(obsdate, na.rm = T),
              q1 = quantile(obsdate, probs = 0.25, type = 1, na.rm = T),
              mean = mean(obsdate, na.rm = T),
              median = quantile(obsdate, probs = 0.5, type = 1, na.rm = T),
              q3 = quantile(obsdate, probs = 0.75, type = 1, na.rm = T),
              max = max(obsdate, na.rm = T))

bmival_df %>% 
    filter(between(value, 10, 70)) %>%
    collect() %>% 
    summarise(n = n(),
              n_na = sum(is.na(obsdate), na.rm = T),
              pre_1995 = sum(obsdate < ymd("1995-01-01"), na.rm = T),
              pre_2013 = sum(obsdate < ymd("2013-04-01"), na.rm = T),
              pre_2015 = sum(obsdate < ymd("2015-04-01"), na.rm = T),
              pre_2018 = sum(obsdate < ymd("2018-04-01"), na.rm = T),
              pre_2020 = sum(obsdate < ymd("2020-04-01"), na.rm = T),
              post_2023 = sum(obsdate > ymd("2023-03-31"), na.rm = T)) %>% 
    pivot_longer(cols = everything(), names_to = "var", values_to = "value") %>% 
    mutate(prop = value/df_nrow)
```

```{r}
bmival_df %>% 
    filter(between(value, 10, 70),
           obsdate >= "1995-01-01") %>% 
    collect() %>%
    mutate(ym = ymd(paste0(year(obsdate), "-", month(obsdate), "-01"))) %>% 
    group_by(ym) %>% 
    summarise(n = n()) %>% 
    ggplot(aes(x = ym, y = n)) +
    geom_bar(stat = "identity") +
    scale_x_date(date_breaks="1 year", date_labels = "%b %Y", limits = c(ymd("1995-01-01", "2023-04-01"))) +
    scale_y_continuous(labels = label_comma()) +
    theme(axis.text.x = element_text(angle=90, vjust=.5, hjust=1)) 
```

### Execute

```{r}
#| eval: false

# Remove records with NA in value
# Drop extreme values - less than 10 and more than 70
# Keep only BMI value records from 2020-04-01 (within three years of end date)
# Categorise BMI

dbExecute(con, "DROP TABLE IF EXISTS p068_bmival_clean;")

bmi_cat_query <- "CREATE TABLE p068_bmival_clean
    WITH t AS (
        SELECT *
        FROM p068_bmival_define
        WHERE value BETWEEN 10 AND 70
        AND obsdate >= '1995-01-01'
        )
        SELECT *,
            CASE 
                WHEN value < 18.5 THEN 'below 18.5 - Underweight'
                WHEN value >= 18.5 AND value < 25 THEN '18.5 to 24.9 - Healthy weight'
                WHEN value >= 25 AND value < 30 THEN '25 to 29.9 - Overweight'
                WHEN value >= 30 AND value < 40 THEN '30 to 39.9 - Obese'
                WHEN value >= 40 THEN '40 or above - Severely obese'
            END AS bmi_category
        FROM t
    ;"

dbExecute(con, bmi_cat_query)
```
```{r}
# Check
tbl(con, "p068_bmival_clean") %>% 
    summarise(n = n(),
              min = min(value, na.rm = T),
              mean = mean(value, na.rm = T),
              max = max(value, na.rm = T),
              n_na = sum(is.na(value), na.rm = T),
              min_date = min(obsdate, na.rm = T),
              mean_date = mean(obsdate, na.rm = T),
              max_date = max(obsdate, na.rm = T),
              n_na_date = sum(is.na(obsdate), na.rm = T))

tbl(con, "p068_bmival_clean") %>% 
    group_by(bmi_category) %>% 
    summarise(n = n(),
              min = min(value, na.rm = T),
              mean = mean(value, na.rm = T),
              max = max(value, na.rm = T))
```



```{r}
# Create separate table for obese people only, combining bmival and obesity tables
dbExecute(con, "DROP TABLE IF EXISTS p068_obesity_mod_factor;")

obesity_combine_query <- "CREATE TABLE p068_obesity_mod_factor
        WITH v AS ( -- Keep records with BMI value above 30 only
            SELECT *
            FROM p068_bmival_clean
            WHERE bmi_category IN ('30 to 39.9 - Obese', '40 or above - Severely obese')
        ),
        u AS ( -- Union obese records from classification and BMI value
            SELECT *, NULL AS bmi_category FROM p068_obese_classification
            UNION
            SELECT * FROM v),
        r AS ( -- Calculate row numbers per patient to keep latest record
            SELECT *,
            ROW_NUMBER() OVER (PARTITION BY patid ORDER BY obsdate DESC) AS rn
            FROM u
        )
        -- Keep latest record per patient
        SELECT
            patid,
            pracid,
            obsid,
            obsdate,
            medcodeid,
            medcodeid_desc,
            value,
            numunitid,
            obstypeid,
            include,
            category,
            cluster_id,
            bmi_category
        FROM r
        WHERE rn = 1;
    "

dbExecute(con, obesity_combine_query)
```

```{r}
# Count number of overlap
dbGetQuery(con, "SELECT COUNT(DISTINCT b.patid)
    FROM (SELECT *
            FROM p068_bmival_clean
            WHERE bmi_category IN ('30 to 39.9 - Obese', '40 or above -     Severely obese')) AS b 
    INNER JOIN p068_obese_classification AS o ON b.patid = o.patid;")
```


```{r}
# Check
tbl(con, "p068_obesity_mod_factor") %>% 
    count(medcodeid_desc) %>% 
    arrange(desc(n))

# Some of the classification codes must have a BMI value associated, therefore max value is not 70 but 108
tbl(con, "p068_obesity_mod_factor") %>% 
    summarise(n = n(),
              n_patid = n_distinct(patid),
              min = min(value, na.rm = T),
              mean = mean(value, na.rm = T),
              max = max(value, na.rm = T),
              n_na = sum(is.na(value), na.rm = T),
              min_date = min(obsdate, na.rm = T),
              mean_date = mean(obsdate, na.rm = T),
              max_date = max(obsdate, na.rm = T),
              n_na_date = sum(is.na(obsdate), na.rm = T))
```


```{r}
# Disconnect database
dbDisconnect(con)
```