---
title: "results"
format: html
---

```{r}
# Set time zone
Sys.setenv(TZ='Europe/London')

# Download and attach standard packages
if (!require(pacman)) {
  install.packages("pacman")
}

pacman::p_load(tidyverse, here, janitor, RMariaDB, DBI, glue, renv, dbplyr, lubridate, scales)

i_am("R/results.qmd")
```

```{r}
# Connect to CPRD database -------------------

# Connect to the MySQL database: con
con <- dbConnect(RMariaDB::MariaDB(), 
                 dbname = "cprd2023", 
                 host = "cprd-sea-2023.cisllnygqz7r.eu-west-2.rds.amazonaws.com", 
                 port = 3306,
                 user = "test",
                 password = "password")
```

```{r}
# Function to populate results for modifiable factors, comorbidities and exclusions
populate_results <- function(var_name, var_type, description, age_45_84) {
    val_43_84 <- dbGetQuery(con, glue("SELECT COUNT(DISTINCT patid) AS n_ppl
	FROM p068_{var_name}_{var_type}
	WHERE patid IN (SELECT patid FROM p068_cohort_43_84)")) %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()
    
    if (age_45_84) {
        val_45_84 <- dbGetQuery(con, glue("SELECT COUNT(DISTINCT patid) AS n_ppl
	FROM p068_{var_name}_{var_type}
	WHERE patid IN (SELECT patid FROM p068_cohort_45_84)")) %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()
    } else {
        val_45_84 <- NA_real_
    }
    
    results <- tibble(variable = var_name, 
                      description = description, 
                      value_aged_43_84 = val_43_84,
                      value_aged_45_84 = val_45_84)
    
    return(results)
}
```

## Cohort

### The number of registered people (all age) as of 31 March 2023

```{r}
all_reg <- dbGetQuery(con, "SELECT COUNT(DISTINCT patid) AS n_ppl
	FROM acceptable_pats_2023_12
	WHERE (regenddate IS NULL OR regenddate > '2023-03-31')
	AND pracid NOT IN ( -- Not in absorbed practices
		SELECT pracid
		FROM absorbed_practices_2023_12);") %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()
```

### The number of people aged 43 to 84 years and 45 to 84 years

```{r}
n_43_84 <- dbGetQuery(con, "SELECT COUNT(DISTINCT patid) AS n_ppl
	FROM p068_cohort_43_84") %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()

n_45_84 <- dbGetQuery(con, "SELECT COUNT(DISTINCT patid) AS n_ppl
	FROM p068_cohort_45_84") %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()
```


```{r}
cohort_numbers <- tibble(variable = c("all_reg", "n_cohort"), 
                            description = c("The number of people registered in CPRD on 31 March 2023, all ages",
                                            "The number of people in that age group registered in CPRD on 31 March 2023"), 
                            value = c(all_reg, NA_real_),
                            value_aged_43_84 = c(NA_real_, n_43_84),
                            value_aged_45_84 = c(NA_real_, n_45_84))
```

## Modifiable risk factors

```{r}
mod_factor_params <- tribble(~var_name, ~var_type, ~description, ~age_45_84,
                       "smoker", "mod_factor", "The number of current smokers", FALSE,
                       "obesity", "mod_factor", "The number who are obese", FALSE,
                       "hypertension", "mod_factor", "The number with hypertension", FALSE,
                       "high_cholesterol", "mod_factor", "The number with high cholesterol", FALSE)

mod_factor_results <- pmap(mod_factor_params, populate_results) %>% bind_rows()
```

## Comorbidities

```{r}
comorbidity_params <- tribble(~var_name, ~var_type, ~description, ~age_45_84,
                       "t2dm", "comorbidity", "The number with type 2 diabetes", FALSE,
                       "erectile_dysfunction", "comorbidity", "The number with erectile dysfunction", FALSE,
                       "smi", "comorbidity", "The number with serious mental illness", FALSE,
                       "rarth", "comorbidity", "The number with rheumatoid arthritis", FALSE,
                       "sle", "comorbidity", "The number with systemic lupus erythematosus", FALSE,
                       "afib", "comorbidity", "The number with atrial fibrillation", FALSE)

comorbidity_results <- pmap(comorbidity_params, populate_results) %>% bind_rows()
```

## Exclusions

```{r}
# CVD risk assessment
cvdriskass_exclusion_val_43_84 <- dbGetQuery(con, glue("SELECT COUNT(DISTINCT patid) AS n_ppl
	FROM p068_cvdriskass_exclusion
	WHERE patid IN (SELECT patid FROM p068_cohort_43_84)")) %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()

cvdriskass_exclusion_val_45_84 <- dbGetQuery(con, glue("SELECT COUNT(DISTINCT patid) AS n_ppl
	FROM p068_cvdriskass_exclusion
	WHERE patid IN (SELECT patid FROM p068_cohort_45_84)")) %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()

cvdriskass_exclusion <- tibble(variable = "cvdriskass",
                  description = "The number with a 10-year CVD risk score of 10% or more prior to 1 April 2018",
                  value_aged_43_84 = cvdriskass_exclusion_val_43_84,
                  value_aged_45_84 = cvdriskass_exclusion_val_45_84)
```

```{r}
exclusion_params <- tribble(~var_name, ~var_type, ~description, ~age_45_84,
                            "t1dm", "exclusion", "The number with type 1 diabetes", TRUE,
                       "cvd", "exclusion", "The number with CVD", TRUE,
                       "fhyp", "exclusion", "The number with familial hypercholesterolaemia", TRUE,
                       "ckd", "exclusion", "The number with CKD stage 3 to 5", TRUE,
                       "llt", "define", "The number who were prescribed lipid lowering therapy in the last 6 months (between 1 October 2022 and 31 March 2023)", TRUE)

exclusion_results <- pmap(exclusion_params, populate_results) %>% bind_rows(cvdriskass_exclusion)
```

## Combinations

```{r}
# Join mod factors and comorbidities to cohort table
dbExecute(con, "DROP TABLE IF EXISTS p068_cohort_43_84_joined;")

join_factors_query <- "CREATE TABLE p068_cohort_43_84_joined
    SELECT p.patid,
            smok.medcodeid AS smoker_medcodeid,
            obes.medcodeid AS obese_medcodeid,
            hyp.medcodeid AS hypertension_medcodeid,
            chol.medcodeid AS high_cholesterol_medcodeid,
            t2dm.medcodeid AS t2dm_medcodeid,
            ed.medcodeid AS erectile_dysfunction_medcodeid,
            smi.medcodeid AS smi_medcodeid,
            rarth.medcodeid AS rarth_medcodeid,
            sle.medcodeid AS sle_medcodeid,
            afib.medcodeid AS afib_medcodeid,
            t1dm.medcodeid AS t1dm_medcodeid,
            cvd.medcodeid AS cvd_medcodeid,
            fhyp.medcodeid AS fhyp_medcodeid,
            ckd.medcodeid AS ckd_medcodeid,
            llt.indexdate AS llt_indexdate,
            cvdriskass.medcodeid AS cvdriskass20_medcodeid,
            cvdriskass_2018.medcodeid AS cvdriskass2018_medcodeid,
            cvdriskass_2018.obsdate AS cvdriskass2018_obsdate,
            nhs_hc.medcodeid AS nhs_health_check2018_medcodeid,
            CASE
                WHEN smok.medcodeid IS NOT NULL
                    OR obes.medcodeid IS NOT NULL
                    OR hyp.medcodeid IS NOT NULL
                    OR chol.medcodeid IS NOT NULL THEN 1
                ELSE 0
            END AS mod_factor,
            CASE
                WHEN smok.medcodeid IS NOT NULL
                    OR obes.medcodeid IS NOT NULL
                    OR hyp.medcodeid IS NOT NULL
                    OR chol.medcodeid IS NOT NULL
                    OR t2dm.medcodeid IS NOT NULL
                    OR ed.medcodeid IS NOT NULL
                    OR smi.medcodeid IS NOT NULL
                    OR rarth.medcodeid IS NOT NULL
                    OR sle.medcodeid IS NOT NULL
                    OR afib.medcodeid IS NOT NULL THEN 1
                ELSE 0
            END AS mod_factor_or_comorbidity,
            CASE
                WHEN t1dm.medcodeid IS NOT NULL
                    OR cvd.medcodeid IS NOT NULL
                    OR fhyp.medcodeid IS NOT NULL
                    OR ckd.medcodeid IS NOT NULL
                    OR llt.indexdate IS NOT NULL
                    OR cvdriskass.medcodeid IS NOT NULL THEN 1
                ELSE 0
            END AS exclusion
        FROM p068_cohort_43_84 AS p
        LEFT JOIN p068_smoker_mod_factor AS smok ON p.patid = smok.patid
        LEFT JOIN p068_obesity_mod_factor AS obes ON p.patid = obes.patid
        LEFT JOIN p068_hypertension_mod_factor AS hyp ON p.patid = hyp.patid
        LEFT JOIN p068_high_cholesterol_mod_factor AS chol ON p.patid = chol.patid
        LEFT JOIN p068_t2dm_comorbidity AS t2dm ON p.patid = t2dm.patid
        LEFT JOIN p068_erectile_dysfunction_comorbidity AS ed ON p.patid = ed.patid
        LEFT JOIN p068_smi_comorbidity AS smi ON p.patid = smi.patid
        LEFT JOIN p068_rarth_comorbidity AS rarth ON p.patid = rarth.patid
        LEFT JOIN p068_sle_comorbidity AS sle ON p.patid = sle.patid
        LEFT JOIN p068_afib_comorbidity AS afib ON p.patid = afib.patid
        LEFT JOIN p068_t1dm_exclusion AS t1dm ON p.patid = t1dm.patid
        LEFT JOIN p068_cvd_exclusion AS cvd ON p.patid = cvd.patid
        LEFT JOIN p068_fhyp_exclusion AS fhyp ON p.patid = fhyp.patid
        LEFT JOIN p068_ckd_exclusion AS ckd ON p.patid = ckd.patid
        LEFT JOIN p068_llt_define AS llt ON p.patid = llt.patid
        LEFT JOIN p068_cvdriskass_exclusion AS cvdriskass ON p.patid = cvdriskass.patid
        LEFT JOIN p068_cvdriskass_2018_2023_latest AS cvdriskass_2018 ON p.patid = cvdriskass_2018.patid
        LEFT JOIN p068_nhs_health_check_2018_2023 AS nhs_hc ON p.patid = nhs_hc.patid;"

dbExecute(con, join_factors_query)
```

```{r}
check <- dbGetQuery(con, "SELECT * FROM p068_cohort_43_84_joined LIMIT 1000;")
```

### The number of people with a modifiable risk factor: current smoker, obesity, hypertension or hypercholesterolemia 

```{r}
any_mod_factor_val_43_84 <- dbGetQuery(con, "SELECT COUNT(DISTINCT patid) AS n_ppl
    FROM p068_cohort_43_84_joined
    WHERE mod_factor = 1;") %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()

any_mod_factor <- tibble(variable = "any_mod_factor",
                  description = "The number with any of the following modifiable risk factors: current smoker, obesity, hypertension or hypercholesterolemia",
                  value_aged_43_84 = any_mod_factor_val_43_84,
                  value_aged_45_84 = NA_real_)
```

### The number of people with a modifiable risk factor or comorbidity: current smoker, obesity, hypertension, hypercholesterolemia, type 2 diabetes, erectile dysfunction, serious mental illness, rheumatoid arthritis, systemic lupus erythematosus or atrial fibrillation.

```{r}
any_mod_factor_or_comorbidity_val_43_84 <- dbGetQuery(con, "SELECT COUNT(DISTINCT patid) AS n_ppl
        FROM p068_cohort_43_84_joined
        WHERE mod_factor_or_comorbidity = 1") %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()

any_mod_factor_or_comorbidity <- tibble(variable = "any_mod_factor_or_comorbidity",
                  description = "The number with any of the following modifiable risk factors or comorbidities: current smoker, obesity, hypertension, hypercholesterolemia, type 2 diabetes, erectile dysfunction, serious mental illness, rheumatoid arthritis, systemic lupus erythematosus or atrial fibrillation",
                  value_aged_43_84 = any_mod_factor_or_comorbidity_val_43_84,
                  value_aged_45_84 = NA_real_)
```

### The number of people with any exclusions: type 1 diabetes, CVD, famililal hypercholesterolaemia, CKD stage 3 to 5, current LLT, previous CVD risk of 20% or more

```{r}
any_exclusion_val_43_84 <- dbGetQuery(con, "SELECT COUNT(DISTINCT patid) AS n_ppl
    FROM p068_cohort_43_84_joined
        WHERE exclusion = 1;") %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()

any_exclusion_val_45_84 <- dbGetQuery(con, "SELECT COUNT(DISTINCT patid) AS n_ppl
    FROM p068_cohort_43_84_joined
        WHERE patid IN (SELECT patid FROM p068_cohort_45_84)
            AND exclusion = 1;") %>% 
    pull(n_ppl) %>% pluck(1) %>% as.numeric()

any_exclusion <- tibble(variable = "any_exclusion",
                  description = "The number with any of the following exclusion factors: type 1 diabetes, CVD, famililal hypercholesterolaemia, CKD stage 3 to 5, current LLT, previous CVD risk of 20% or more",
                  value_aged_43_84 = any_exclusion_val_43_84,
                  value_aged_45_84 = any_exclusion_val_45_84)
```

## Age 45 to 84 indicator - IND2023-164

The number of people with no exclusion, with a recorded CVD risk assessment score in the preceding 5 years.

```{r}
cvdriskass2018_val_45_84 <- dbGetQuery(con, "SELECT COUNT(DISTINCT patid) AS n_ppl
    FROM p068_cohort_43_84_joined
    WHERE patid IN (SELECT patid FROM p068_cohort_45_84)
    AND exclusion = 0
    AND cvdriskass2018_medcodeid IS NOT NULL;") %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()
```

The number of people with no exclusion, had an NHS health check and have a recorded CVD risk assessment score in the preceding 5 years.

```{r}
cvdriskass2018_nhshc_val_45_84 <- dbGetQuery(con, "SELECT COUNT(DISTINCT patid) AS n_ppl
    FROM p068_cohort_43_84_joined
    WHERE patid IN (SELECT patid FROM p068_cohort_45_84)
    AND exclusion = 0
    AND cvdriskass2018_medcodeid IS NOT NULL
    AND nhs_health_check2018_medcodeid IS NOT NULL;") %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()
```

The number of people with no exclusion, with a recorded CVD risk assessment score in the preceding 3 years.

```{r}
cvdriskass2020_val_45_84 <- dbGetQuery(con, "SELECT COUNT(DISTINCT patid) AS n_ppl
    FROM p068_cohort_43_84_joined
    WHERE patid IN (SELECT patid FROM p068_cohort_45_84)
    AND exclusion = 0
    AND cvdriskass2018_obsdate >= '2020-04-01';") %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()
```


The number of people, with no exclusion, with a recorded CVD risk assessment score in the preceding 1 years.

```{r}
cvdriskass2022_val_45_84 <- dbGetQuery(con, "SELECT COUNT(DISTINCT patid) AS n_ppl
    FROM p068_cohort_43_84_joined
    WHERE patid IN (SELECT patid FROM p068_cohort_45_84)
    AND exclusion = 0
    AND cvdriskass2018_obsdate >= '2022-04-01';") %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()
```

```{r}
result_45_84 <- tibble(variable = c("cvdriskass2018",
                                        "cvdriskass2018_nhshc",
                                        "cvdriskass2020",
                                        "cvdriskass2022"),
                  description = c("The number of people with no exclusion, with a recorded CVD risk assessment score in the preceding 5 years",
                                  "The number of people with no exclusion, had an NHS health check and have a recorded CVD risk assessment score in the preceding 5 years",
                                  "The number of people with no exclusion, with a recorded CVD risk assessment score in the preceding 3 years",
                                  "The number of people, with no exclusion, with a recorded CVD risk assessment score in the preceding 1 years"),
                  value_aged_43_84 = rep(NA_real_, 4),
                  value_aged_45_84 = c(cvdriskass2018_val_45_84,
                                       cvdriskass2018_nhshc_val_45_84,
                                       cvdriskass2020_val_45_84,
                                       cvdriskass2022_val_45_84))
```


## Age 43 to 84 indicator - IND2023-165 and IND2023-166

The number of people, with no exclusion and a modifiable risk factor or comorbidity, with a recorded CVD risk assessment score in the preceding 3 years.

```{r}
cvdriskass2020_mod_comorb_val_43_84 <- dbGetQuery(con, "SELECT COUNT(DISTINCT patid) AS n_ppl
    FROM p068_cohort_43_84_joined
    WHERE mod_factor_or_comorbidity = 1
    AND exclusion = 0
    AND cvdriskass2018_obsdate >= '2020-04-01';") %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()
```

The number of people, with no exclusion and a modifiable risk factor, with a recorded CVD risk assessment score in the preceding 3 years.

```{r}
cvdriskass2020_mod_val_43_84 <- dbGetQuery(con, "SELECT COUNT(DISTINCT patid) AS n_ppl
    FROM p068_cohort_43_84_joined
    WHERE mod_factor = 1
    AND exclusion = 0
    AND cvdriskass2018_obsdate >= '2020-04-01';") %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()
```

The number of people who are current smokers, with no exclusion, with a recorded CVD risk assessment score in the preceding 3 years.

```{r}
cvdriskass2020_smoker_val_43_84 <- dbGetQuery(con, "SELECT COUNT(DISTINCT patid) AS n_ppl
    FROM p068_cohort_43_84_joined
    WHERE smoker_medcodeid IS NOT NULL
    AND exclusion = 0
    AND cvdriskass2018_obsdate >= '2020-04-01';") %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()
```

The number of people who are obese, with no exclusion, with a recorded CVD risk assessment score in the preceding 3 years.

```{r}
cvdriskass2020_obese_val_43_84 <- dbGetQuery(con, "SELECT COUNT(DISTINCT patid) AS n_ppl
    FROM p068_cohort_43_84_joined
    WHERE obese_medcodeid IS NOT NULL
    AND exclusion = 0
    AND cvdriskass2018_obsdate >= '2020-04-01';") %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()
```

The number of people with hypertension, with no exclusion, with a recorded CVD risk assessment score in the preceding 3 years.

```{r}
cvdriskass2020_hyp_val_43_84 <- dbGetQuery(con, "SELECT COUNT(DISTINCT patid) AS n_ppl
    FROM p068_cohort_43_84_joined
    WHERE hypertension_medcodeid IS NOT NULL
    AND exclusion = 0
    AND cvdriskass2018_obsdate >= '2020-04-01';") %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()
```

The number of people with hypercholesterolemia, with no exclusion, with a recorded CVD risk assessment score in the preceding 3 years.

```{r}
cvdriskass2020_chol_val_43_84 <- dbGetQuery(con, "SELECT COUNT(DISTINCT patid) AS n_ppl
    FROM p068_cohort_43_84_joined
    WHERE high_cholesterol_medcodeid IS NOT NULL
    AND exclusion = 0
    AND cvdriskass2018_obsdate >= '2020-04-01';") %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()
```

The number of people with type 2 diabetes, with no exclusion, with a recorded CVD risk assessment score in the preceding 3 years.

```{r}
cvdriskass2020_t2dm_val_43_84 <- dbGetQuery(con, "SELECT COUNT(DISTINCT patid) AS n_ppl
    FROM p068_cohort_43_84_joined
    WHERE t2dm_medcodeid IS NOT NULL
    AND exclusion = 0
    AND cvdriskass2018_obsdate >= '2020-04-01';") %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()
```

The number of people with erectile dysfunction, with no exclusion, with a recorded CVD risk assessment score in the preceding 3 years.

```{r}
cvdriskass2020_ed_val_43_84 <- dbGetQuery(con, "SELECT COUNT(DISTINCT patid) AS n_ppl
    FROM p068_cohort_43_84_joined
    WHERE erectile_dysfunction_medcodeid IS NOT NULL
    AND exclusion = 0
    AND cvdriskass2018_obsdate >= '2020-04-01';") %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()
```

The number of people with serious mental illness, with no exclusion, with a recorded CVD risk assessment score in the preceding 3 years.

```{r}
cvdriskass2020_smi_val_43_84 <- dbGetQuery(con, "SELECT COUNT(DISTINCT patid) AS n_ppl
    FROM p068_cohort_43_84_joined
    WHERE smi_medcodeid IS NOT NULL
    AND exclusion = 0
    AND cvdriskass2018_obsdate >= '2020-04-01';") %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()
```

The number of people with rheumatoid arthritis, with no exclusion, with a recorded CVD risk assessment score in the preceding 3 years.

```{r}
cvdriskass2020_rarth_val_43_84 <- dbGetQuery(con, "SELECT COUNT(DISTINCT patid) AS n_ppl
    FROM p068_cohort_43_84_joined
    WHERE rarth_medcodeid IS NOT NULL
    AND exclusion = 0
    AND cvdriskass2018_obsdate >= '2020-04-01';") %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()
```

The number of people with systemic lupus erythematosus, with no exclusion, with a recorded CVD risk assessment score in the preceding 3 years.

```{r}
cvdriskass2020_sle_val_43_84 <- dbGetQuery(con, "SELECT COUNT(DISTINCT patid) AS n_ppl
    FROM p068_cohort_43_84_joined
    WHERE sle_medcodeid IS NOT NULL
    AND exclusion = 0
    AND cvdriskass2018_obsdate >= '2020-04-01';") %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()
```

The number of people with atrial fibrillation, with no exclusion, with a recorded CVD risk assessment score in the preceding 3 years.

```{r}
cvdriskass2020_afib_val_43_84 <- dbGetQuery(con, "SELECT COUNT(DISTINCT patid) AS n_ppl
    FROM p068_cohort_43_84_joined
    WHERE afib_medcodeid IS NOT NULL
    AND exclusion = 0
    AND cvdriskass2018_obsdate >= '2020-04-01';") %>% pull(n_ppl) %>% pluck(1) %>% as.numeric()
```

```{r}
result_43_84 <- tibble(variable = c("cvdriskass2020_mod_comorb",
                                    "cvdriskass2020_mod",
                                    "cvdriskass2020_smoker",
                                    "cvdriskass2020_obese",
                                    "cvdriskass2020_hyp",
                                    "cvdriskass2020_chol",
                                    "cvdriskass2020_t2dm",
                                    "cvdriskass2020_ed",
                                    "cvdriskass2020_smi",
                                    "cvdriskass2020_rarth",
                                    "cvdriskass2020_sle",
                                    "cvdriskass2020_afib"
                                    ),
                  description = c("The number of people, with no exclusion and a modifiable risk factor or comorbidity, with a recorded CVD risk assessment score in the preceding 3 years",
                                  "The number of people, with no exclusion and a modifiable risk factor, with a recorded CVD risk assessment score in the preceding 3 years",
                                  "The number of people who are current smokers, with no exclusion, with a recorded CVD risk assessment score in the preceding 3 years",
                                  "The number of people who are obese, with no exclusion, with a recorded CVD risk assessment score in the preceding 3 years",
                                  "The number of people with hypertension, with no exclusion, with a recorded CVD risk assessment score in the preceding 3 years", 
                                  "The number of people with hypercholesterolemia, with no exclusion, with a recorded CVD risk assessment score in the preceding 3 years",
                                  "The number of people with type 2 diabetes, with no exclusion, with a recorded CVD risk assessment score in the preceding 3 years",
                                  "The number of people with erectile dysfunction, with no exclusion, with a recorded CVD risk assessment score in the preceding 3 years",
                                  "The number of people with serious mental illness, with no exclusion, with a recorded CVD risk assessment score in the preceding 3 years",
                                  "The number of people with rheumatoid arthritis, with no exclusion, with a recorded CVD risk assessment score in the preceding 3 years",
                                  "The number of people with systemic lupus erythematosus, with no exclusion, with a recorded CVD risk assessment score in the preceding 3 years",
                                  "The number of people with atrial fibrillation, with no exclusion, with a recorded CVD risk assessment score in the preceding 3 years"),
                  value_aged_43_84 = c(cvdriskass2020_mod_comorb_val_43_84,
                                       cvdriskass2020_mod_val_43_84,
                                       cvdriskass2020_smoker_val_43_84,
                                       cvdriskass2020_obese_val_43_84,
                                       cvdriskass2020_hyp_val_43_84,
                                       cvdriskass2020_chol_val_43_84,
                                       cvdriskass2020_t2dm_val_43_84,
                                       cvdriskass2020_ed_val_43_84,
                                       cvdriskass2020_smi_val_43_84,
                                       cvdriskass2020_rarth_val_43_84,
                                       cvdriskass2020_sle_val_43_84,
                                       cvdriskass2020_afib_val_43_84
                                       ),
                  value_aged_45_84 = rep(NA_real_, 12))
```

# Write data

```{r}
results <- bind_rows(cohort_numbers, mod_factor_results, comorbidity_results, any_mod_factor, any_mod_factor_or_comorbidity, exclusion_results, any_exclusion, result_45_84, result_43_84) %>% 
    mutate(across(starts_with("value"), \(x) round(x/5)*5))
```


```{r}
# Write csv
results %>% 
    select(-variable) %>% 
    write_csv(here("data", "068_cvd_indicator_results.csv"),
              na = "",
              quote = "all")
```


```{r}
# Disconnect from database
dbDisconnect(con)
```

